R Markdown for Reproducible Research

### 2019-01-06 paper.Rmd
start section on r notebooks

Code chunks are much like inline code, but they stand alone and are more useful for
lengthier code blocks that do complex logic, setup, value preparation, plotting, or
other output generation.

@@

@@

>>>>

Code chunks are much like inline code, but they stand alone and are more useful for
lengthier code blocks that do complex logic, setup, value preparation, plotting, or
other output generation. It is worth noting that code chunks are [very flexible](todo)
in their options and defaults, and the number of options can sometimes be overwhelming.

@@

When creating a new document in the RStudio IDE, you might notice an option
to create a "R Notebook" or "R Markdown Notebook." This is offered in addition
to the long-known "R Markdown," and the differences are subtle.

![RStudio IDE New File Dropdown showing R Markdown and R Notebook
options](./img/new-file-dropdown.png)

@@

# TIPS AND TRICKS

- Code chunk options
- Knit options
- URLs and internal links
- RStudio documentation, etc
